---
title: "NCBI - SRA"
output: rmarkdown::html_document
vignette: >
  %\VignetteIndexEntry{NCBI - SRA}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
  
<style>
  
  table {
    border: 1px solid gray;
  }

td, th {
  border: 1px solid gray;
  padding: 5px 5px 5px 5px;
}

</style>

<script type="text/javascript">
  
  function ToggleOperation(id) {
    var x = document.getElementById(id+"-block");
    if (x.style.display === "none") {
      x.style.display = "block";
    } else {
      x.style.display = "none";
    }
  }

</script>

```{r, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
# R libraries
library(knitr) # for html table
library(tidyverse) # for pipe
library(yaml)  # for yaml file

# Read in the DESCRIPTION file
description <- yaml::read_yaml("../DESCRIPTION")

# Define variables
program <- description$Package

# Define github repo
github_repo <- description$URL

# Define github pages URL
github_pages_url <- description$GITHUB_PAGES

# Read in files
sra_options_df <- read.csv("./data/sra_experiments_run_list.csv", header=TRUE)

instrument_model_df <- sra_options_df %>% select(instrument_model) %>% 
  dplyr::filter(!instrument_model %in% c(NA, "", NULL) )

library_strategy_df <- sra_options_df %>% select(library_strategy) %>% 
  dplyr::filter(!library_strategy %in% c(NA, "", NULL) )

library_source_df <- sra_options_df %>% select(library_source) %>% 
  dplyr::filter(!library_source %in% c(NA, "", NULL) )

library_selection_df <- sra_options_df %>% select(library_selection) %>% 
  dplyr::filter(!library_selection %in% c(NA, "", NULL) )
```

## Metadata Options

- ### <a onclick="ToggleOperation('instrument-model')">instrument_model</a>

<div id="instrument-model-block" style="display: none;">

```{r include=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
knitr::kable(instrument_model_df, format = "html", row.names = FALSE, col.names=NULL, escape = FALSE)
```

</div>

- ### <a onclick="ToggleOperation('library-strategy')">library_strategy</a>

<div id="library-strategy-block" style="display: none;">

```{r include=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
knitr::kable(library_strategy_df, format = "html", row.names = FALSE, col.names=NULL, escape = FALSE)
```

</div>

- ### <a onclick="ToggleOperation('library-source')">library_source</a>

<div id="library-source-block" style="display: none;">


```{r include=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
knitr::kable(library_source_df, format = "html", row.names = FALSE, col.names=NULL, escape = FALSE)
```

</div>

- ### <a onclick="ToggleOperation('library-selection')">library_selection</a>

<div id="library-selection-block" style="display: none;">

```{r include=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
knitr::kable(library_selection_df, format = "html", row.names = FALSE, col.names=NULL, escape = FALSE)
```

</div>


<br><br><br>

Any questions or issues? Please report them on our <a href="`r github_repo`/issues" target="_blank">Github issue tracker</a>.

<br>


















